### 2019-07-26 paper/paper.tex
Update paper.tex

The aim of this paper is twofold. The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

@@

As Hal Varian emphasizes, there is a need for mutual collaboration between machine learning developers/practitioners and econometricians. In this paper we describe a research-project aimed at building bridges between machine learning and econometric worlds and introduce the main characteristics of its first outcome: a Julia-native all-subset regression algorithm (\verb GlobalSearchRegression.jl)  which runs up to 3165 and 197 times faster than existing Stata and R alternatives, respectively. \vskip 6pt

>>>>

The aim of this paper is twofold. The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds (\verb ModelSelection.jl). The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

@@

As Hal Varian emphasizes, there is a need for mutual collaboration between machine learning developers/practitioners and econometricians. In this paper we describe a research-project aimed at building bridges between machine learning and econometric worlds (\verb ModelSelection.jl) and introduce the main characteristics of its first outcome: a Julia-native all-subset regression algorithm (\verb GlobalSearchRegression.jl)  which runs up to 3165 and 197 times faster than existing Stata and R alternatives, respectively. \vskip 6pt
